NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-19 results.tex
few mods

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (red) and NLO \QCDtEW\ (black) 
    including scale uncertainties. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying any jet veto, while the centre ratio plot 
    applies a jet veto of $p_\mathrm{T}^\mathrm{veto}=\text{30\,GeV}$. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.\\
    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaw:myy}
  }
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (red) and NLO \QCDtEW\ (black) 
    including scale uncertainties. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying any jet veto, while the centre ratio plot 
    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.\\
    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaw:myy}
  }
\end{figure}
